`r params$doc_title`

### 2023-04-19 scripts/MSc.Rmd
small changes

>>>>

# References

<div id="refs"></div>

# Software

This analysis was carried out using the statistical software `r base::version$version.string`.

Apart from R's base functionality, the following packages were used: <br/>

```{r software, echo=FALSE}
# or faster with function...
installed.packages()[names(sessionInfo()$otherPkgs), "Version"]
# map(names(sessionInfo()$otherPkgs), ~citation(.x))
```
